### 2019-03-14 _publications/jors/paper.tex
more changes
Copy of paper ready for Trevor

@@

\begin{itemize}
  \item Build the Nix environment from a cached storage reducing the
    build time.
  \item Run automated tests on Jupyter Notebooks using
    NBval~\cite{nbval} and Py.test~\cite{pytest}.
  \item Lint and test front-end Coffeescript using appropriate tools.
  \item Display a temporary version of the website using
    Surge~\cite{surge} for visual review.
\end{itemize}

@@

\begin{description}[noitemsep,topsep=0pt]
	\item[Name:] GitHub
	\item[Persistent identifier:] \url{https://github.com/usnistgov/pfhub/tree/v0.1}
	\item[Licence:] NIST Public Domain License~\cite{nistlicense}
	\item[Date published:] 13/03/19
\end{description}

@@

\textcolor{blue}{Please describe in as much detail as possible the
  ways in which the software could be reused by other researchers both
  within and outside of your field. This should include the use cases
  for the software, and also details of how the software might be
  modified or extended (including how contributors should contact you)
  if appropriate. Also you must include details of what support
  mechanisms are in place for this software (even if there is no
  support).}

@@

\textcolor{blue}{Please add any relevant acknowledgments to anyone
  else who supported the project in which the software was created,
  but did not work directly on the software itself.}

@@

\textcolor{blue}{If the software resulted from funded research please
  give the funder and grant number.}

>>>>

\url{https://pages.nist.gov/pfhub}

@@

\begin{itemize}
  \item Build the Nix environment from a cached storage reducing the
    build time.
  \item Run automated tests on Jupyter Notebooks using
    NBval~\cite{nbval} and Py.test~\cite{pytest}.
  \item Run validation tests on HTML files using
    HTMLProofer~\cite{htmlproofer}.
  \item Lint and test front-end Coffeescript using appropriate tools.
  \item Display a temporary version of the website using
    Surge~\cite{surge} for visual review.
\end{itemize}

@@

\begin{description}[noitemsep,topsep=0pt]
	\item[Name:] GitHub
	\item[Persistent identifier:] \url{https://github.com/usnistgov/pfhub/tree/v0.1}
	\item[Licence:] NIST Software License~\cite{nistlicense}
	\item[Date published:] 13/03/19
\end{description}

@@

The website infrastructure can be forked and deployed with minimum
effort including the upload mechanism using Staticman. However,
customizing the website for a particular scientific community would
require considerable effort. The following steps are the more
challenging aspects of deploying the framework for a new community.

\begin{itemize}
  \item Edit or upload new Jupyter Notebooks with benchmark or data
    requirement descriptions.
  \item Edit the \texttt{benchmarks.yaml} file to reflect the new
    upload requirements and describe the figures that need to be
    generated on the upload comparison pages.
  \item Edit the \texttt{\_config.yml} file to update links and text
    related to the configuration for all aspects of the website.
  \item Update Markdown files to reflect the new content and mission
    of the scientific community.
  \item Remove data and files that are not required by the new
    community.
\end{itemize}

Currently, a deployment for a new community has not been attempted
and, thus, the above steps need to be refined and documented.

@@

We gratefully acknowledge input and guidance from all participants in
the series of Phase-Field workshops held between 2015 and 2018 at the
Center for Hierarchical Material Design~\cite{workshops}.

@@

Ask Jim for this text.
